\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\input{glyphtounicode}

% -------------------- FONT OPTIONS --------------------
% sans-serif
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% serif
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in} % Default was -.5in
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{2.08003pt}

% -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- HEADING--------------------
\begin{flushright}
  \color{gray}
  \item
\end{flushright}

\vspace{-16.5pt}

\begin{center}
    \textbf{\Huge \scshape Aditya} \\ \vspace{8pt}
    \small 
    \faIcon{briefcase}                     
    \href{https://www.adityapujer.xyz}
    {\underline{adityapujer.xyz}}
    \faIcon{phone}
    \href{tel:+917204328987}
    {\underline{+91 7204318987}}
    \faIcon{github}
    \href{https://github.com/aditzz073}{\underline{github.com/aditzz073}} $  $
    \faIcon{linkedin}
    \href{https://linkedin.com/in/aditya-pujer}{\underline{in/aditya-pujer}} $  $
    \faIcon{envelope}
    \href{mailto:pujeradi@gmail.com}
    {\underline{pujeradi@gmail.com}}
    
\end{center}

% -------------------- EDUCATION --------------------
\section{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Dayananda Sagar College of Engineering}{Sept. 2027}
      {B.E. Information Science}{CGPA: 9.15}
  \resumeSubHeadingListEnd
% -------------------- SKILLS --------------------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    
     \textbf{Languages}{: Javascript, Typescript, Python} \\
     \textbf{Frameworks and Libraries}{: Node.js, Express, Next.js} \\
     
     \textbf{Tools}{: Git, GitHub Actions,GitOps}     
     
    }}
 \end{itemize}
 \vspace{-15pt}
 
% -------------------- EXPERIENCE --------------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{\href{https://wecofy.com/}{\underline{FreeSip}}}{January 2025 – May 2025}
{Full-Stack Developer: Next.js, Node.js, Express, Tailwind CSS}{Intern · Onsite}
\resumeItemListStart
  \resumeItem{Worked on \textbf{FreeSip}, focusing on a \textbf{ B2B marketing platform}, and building responsive UIs using \textbf{React, Vite, and Tailwind CSS}.}
  \resumeItem{Implemented component-based architecture with effective state management and integrated \textbf{Framer Motion} for smooth UI animations and transitions.}
  \resumeItem{Gained experience in full-stack workflows, interactive user experience design, and customized promotional website features for enhanced user engagement}
  % \resumeItem{Implemented dynamic \textbf{rate-limiting} based on subscription levels, ensuring system \textbf{efficiency} and \textbf{fair usage}.}
\resumeItemListEnd
  
  \resumeItemListEnd




\vspace{-6pt}

% -------------------- PROJECTS --------------------
\section{Projects}
    \resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{EmberEye: AI-Powered Wildfire Risk Prediction} $|$ \footnotesize\emph{Tensorflow, CNN, FastAPI, Python}}
{\faIcon{github}\href{https://github.com/aditzz073/ember-eye}{ \underline{Repo}}  \faIcon{link}\href{https://embereye-three.vercel.app/}{ \underline{Demo}}}
\resumeItemListStart
    \resumeItem{Developed an AI system to predict and visualize wildfire risks based on environmental factors and real-time weather data.}
    \resumeItem{Built a machine learning pipeline using \textbf{Tensorflow} and \textbf{CNN models} to analyze input features and generate risk scores.}
    \resumeItem{Created REST APIs with \textbf{FastAPI} to serve predictions and integrated them into an interactive web dashboard.}
    \resumeItem{Enabled proactive decision-making for communities by providing clear risk visualizations and preventive insights.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Trash View On Maps} $|$ \footnotesize\emph{Google Maps API, Node.js, Google Street View API}}
{\faIcon{github}\href{https://github.com/aditzz073/Trash-view-on-maps}{ \underline{Repo}}  \faIcon{link}\href{https://trash-view-on-maps.vercel.app/}{ \underline{Demo}}}
\resumeItemListStart
    \resumeItem{Built an interactive web game that lets players explore random street view locations from top Indian cities and identify visible trash.}
    \resumeItem{Leveraged the \textbf{Google Maps} and \textbf{Street View APIs} to dynamically load locations and capture user feedback.}
    \resumeItem{Implemented the backend in \textbf{Node.js}, handling location data rotation and storing user responses for future analysis.}
    \resumeItem{Aimed to crowdsource urban cleanliness data and create awareness through gamification.}
\resumeItemListEnd


\resumeProjectHeading
{\textbf{KisanSetu} $|$ \footnotesize\emph{Node.js, Express, WebSocket, Solidity, Docker, Firebase}}
{\faIcon{github}\href{https://github.com/slashexx/kisansetu}{ \underline{Repo}}  \faIcon{link}\href{https://kisansetu.onrender.com}{ \underline{Demo}}}

\resumeItemListStart
    \resumeItem{Developed a blockchain platform for secure contract farming agreements between farmers and buyers.}
    \resumeItem{Integrated \textbf{smart contracts} in \textbf{Solidity} for transparent and reliable transactions.}
    \resumeItem{Implemented features like \textbf{real-time price negotiation}, \textbf{direct communication}, and \textbf{automated payments}.}
    \resumeItem{Deployed the application with \textbf{Docker} and used \textbf{Firebase} for authentication and data management. }
\resumeItemListEnd

    \resumeSubHeadingListEnd
\vspace{-9.5pt}


% -------------------- EXTRA-CURRICULAR --------------------

\section{Extracurricular} \vspace{0.5pt}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=0.08em, topsep=1pt]
    \item \textbf{Team Lead, Mudita, DSI} (Nov 2023 – Present): 
    Event photographer capturing community projects like Valuable Vintage and Pawsitivity, managing social media, promoting ethics and impact through visual storytelling.

    \item \textbf{Technical Team Member, Genesis, ISE} (Nov 2024 – Present): 
    Organized initiatives like Hackman (24hr Hackathon) and Catalysis (technical fest), handling event management and innovating technical solutions.

    \item \textbf{AGMTA:} Maths Quiz Winner (2018).

    \item \textbf{State-Level Gold:} Athletics, Football \& Rope Skipping.
\end{itemize}
\end{document}
