\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\input{glyphtounicode}

% -------------------- FONT OPTIONS --------------------
% sans-serif
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% serif
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in} % Default was -.5in
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{2.08003pt}

% -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- HEADING--------------------
\begin{flushright}
  \color{gray}
  \item
\end{flushright}

\vspace{-16.5pt}

\begin{center}
    \textbf{\Huge \scshape Aditya} \\ \vspace{8pt}
    \small 
                      
    \href{https://www.adityapujer.xyz}
    {\underline{adityapujer.xyz}}
    $ | $
    \href{tel:+917204328987}
    {\underline{+91 7204318987}}
    $ | $
    \href{https://github.com/aditzz073}{\underline{github.com/aditzz073}} $  $
    $ | $
    \href{https://linkedin.com/in/aditya-pujer}{\underline{in/aditya-pujer}} $  $
    $ | $
    \href{mailto:pujeradi@gmail.com}
    {\underline{pujeradi@gmail.com}}
    
\end{center}

% -------------------- EDUCATION --------------------
\section{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Dayananda Sagar College of Engineering}{Sept. 2027}
      {B.E. Information Science}{CGPA: 9.15}
  \resumeSubHeadingListEnd

  % -------------------- PROFESSIONAL SUMMARY --------------------
\section{Professional Summary}
\resumeSubHeadingListStart
  \resumeSubheading
    {\normalfont Proactive undergraduate with startup founder experience. Skilled in research, operations, client relations, and\\
      basic programming (JavaScript/Python). Available for full-time, in-person work in HSR Layout supporting\\
      founders with scheduling, research, presentations, and light technical tasks.\\}{}{}{}

\resumeSubHeadingListEnd
\vspace{-1.6em}

 
% -------------------- EXPERIENCE --------------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{\href{https://freesipindia.xyz/}{\underline{FreeSip India}}}{January 2025 – May 2025}
{Founder \& CTO}{Onsite}
\resumeItemListStart
  \resumeItem{Co-founded and led both technical and operational execution for FreeSip, a B2B marketing startup distributing branded bottled water at large public events.}
  \resumeItem{Managed client relationships, coordinated meetings, and oversaw deliverables, achieving successful execution of FreeSip’s first large-scale project with strong brand impact and profitability.}
  \resumeItem{Conducted market and competitor research to identify high-potential branding channels and event distribution strategies.}
  \resumeItem{Created and presented persuasive pitch decks that secured three clients and two sponsorship opportunities through proactive outreach at Bengaluru tech and business networking events.}
  \resumeItem{Handled cross-functional responsibilities including product development, vendor coordination, logistics, and branding, ensuring seamless execution under tight timelines.}
\resumeItemListEnd

\resumeSubHeadingListEnd


\vspace{-10pt}


% -------------------- SKILLS --------------------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Languages \& Frameworks}{: JavaScript, TypeScript, Python, Next.js} \\
        \textbf{Tools \& Platforms}{: Notion, Trello, Slack, Asana, Git, GitHub} \\
        \textbf{Core Strengths}{: Research \& Analysis, Team Coordination, Client Relations, Pitch Deck Development, Event Logistics, Problem-Solving, Startup Operations} 
    }}
\end{itemize}
\vspace{-15pt}



% -------------------- PROJECTS --------------------
\section{Projects}
    \resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{EmberEye: AI-Powered Wildfire Risk Prediction} }
{\faIcon{github}\href{https://github.com/aditzz073/ember-eye}{ \underline{Repo}}  \faIcon{link}\href{https://embereye-three.vercel.app/}{ \underline{Demo}}}
\resumeItemListStart
    \resumeItem{Built and deployed an AI-powered dashboard that predicts wildfire risks using environmental and weather data, enabling proactive decision-making.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Trash View On Maps} }
{\faIcon{github}\href{https://github.com/aditzz073/Trash-view-on-maps}{ \underline{Repo}}  \faIcon{link}\href{https://trash-view-on-maps.vercel.app/}{ \underline{Demo}}}
\resumeItemListStart
    \resumeItem{Developed a gamified web platform to crowdsource urban waste identification through street view imagery, managing the project from concept to launch.}
\resumeItemListEnd
\vspace{-4.5pt}


%----------------- LEADERSHIP & OPERATIONS HIGHLIGHTS -----------------
\section{Leadership \& Operations Highlights}
\resumeItemListStart
    \resumeItem{\textbf{Event Logistics} — Media Lead at Mudita NGO, managing a 25-member team for event promotions and social media campaigns with measurable engagement growth.}
    \resumeItem{\textbf{Hackathon Team Lead} — Led 2 hackathon teams to “Most Innovative Project” awards, coordinating deadlines, team workflows, and presentations.}
    \resumeItem{\textbf{Project Management Tools} — Proficient in Notion, Trello, Slack, and Asana for task tracking, coordination, and reporting.}
    \resumeItem{\textbf{Research \& Analysis} — Conducted market, competitor, and tech research for projects like KisanSetu, ReconGraph, and wildfire prediction models.}
\resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-9.5pt}


% -------------------- SELECTED ACHIEVEMENTS --------------------
\section{Achievements}
\resumeItemListStart
  \resumeItem{Secured \textbf{3 paying clients} and \textbf{2 sponsorship leads} for FreeSip through \textbf{cold pitching} at networking events.}
  \resumeItem{Won \textbf{“Most Innovative Project”} in 2 hackathons for \textbf{problem-solving} and \textbf{creative execution}.}
  \resumeItem{Coordinated \textbf{multi-channel event campaigns} for Mudita NGO, achieving measurable \textbf{reach and engagement growth}.}
\resumeItemListEnd
\vspace{-0.2em}


\end{document}