\documentclass[letterpaper,11pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\input{glyphtounicode}

% -------------------- FONT OPTIONS --------------------
% sans-serif
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% serif
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in} % Default was -.5in
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{2.08003pt}

% -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- HEADING--------------------
\begin{flushright}
  \color{gray}
  \item
\end{flushright}

\vspace{-16.5pt}

\begin{center}
    \textbf{\Huge \scshape Aditya} \\ \vspace{8pt}
    \small 
    \faIcon{briefcase}                  
    \href{https://www.adityapujer.xyz}
    {\underline{adityapujer.xyz}}
    $ | $
    \faIcon{phone}
    \href{tel:+917204328987}
    {\underline{+91 7204318987}}
    $ | $
    \faIcon{github}
    \href{https://github.com/aditzz073}{\underline{github.com/aditzz073}} $  $
    $ | $
    \faIcon{linkedin}
    \href{https://linkedin.com/in/aditya-pujer}{\underline{in/aditya-pujer}} $  $
    $ | $
    \faIcon{envelope}
    \href{mailto:pujeradi@gmail.com}
    {\underline{pujeradi@gmail.com}}
    
\end{center}

% -------------------- EDUCATION --------------------
\section{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Dayananda Sagar College of Engineering}{Sept. 2027}
      {B.E. Information Science}{CGPA: 9.15}
  \resumeSubHeadingListEnd

% -------------------- SKILLS --------------------
\section{Skills}

\begin{itemize}[leftmargin=0.15in,label={}]

\small{\item{

\textbf{Languages:} Python, JavaScript, TypeScript, C/C++ \\

\textbf{Technologies:} React, Next.js, TailwindCSS, Vite, React Flow, Node.js, Express, FastAPI, REST APIs \\

\textbf{Databases \& Infrastructure:} PostgreSQL, MongoDB, Redis, Docker, Docker Compose \\

\textbf{Tools:} Git, GitHub, GitHub Actions, Google Workspace \\

\textbf{Project Skills:} Project Coordination, Documentation, Team Collaboration, Problem Solving, Stakeholder Communication \\
}}

\end{itemize}

\vspace{-10pt}

% EXPERIENCE

\section{Experience}

\resumeSubHeadingListStart

\resumeSubheading
{\href{https://www.freesipindia.xyz}{\underline{FreeSip India}}}{Jan 2025 -- May 2025}
{Full Stack Developer Intern}{Onsite}

\resumeItemListStart

\resumeItem{Contributed to the development and implementation of features for a B2B marketing platform focused on event-based brand engagement initiatives.}

\resumeItem{Collaborated on translating project requirements into actionable deliverables while working across design and development workflows.}

\resumeItem{Participated in iterative project execution, adapting to evolving requirements and delivering improvements within defined timelines.}

\resumeItemListEnd

\resumeSubHeadingListEnd

% -------------------- LEADERSHIP --------------------

\section{Leadership \& Activities}

\begin{itemize}[leftmargin=0.15in,label={},itemsep=1pt,topsep=0pt]

\item
\textbf{Team Head -- Mudita, DSI}
\hfill
\textit{Nov 2023 -- Present}

\vspace{-5pt}

\begin{itemize}[leftmargin=0.2in,itemsep=0pt]
\item Led community initiatives by coordinating team activities, managing outreach efforts, and supporting project execution through content and social media initiatives.
\end{itemize}

\vspace{-6pt}

\item
\textbf{Technical Team Head -- Genesis ISE}
\hfill
\textit{Nov 2024 -- Present}

\vspace{-5pt}

\begin{itemize}[leftmargin=0.2in,itemsep=0pt]
\item Contributed to planning and execution of technical events including Hackman and Catalysis while collaborating with teams to ensure smooth coordination.
\end{itemize}

\vspace{-6pt}

\item
\textbf{Achievements:}
AGMTA Mathematics Quiz Winner • State-Level Gold in Athletics, Football, and Rope Skipping

\end{itemize}

\vspace{-10pt}

% -------------------- PROJECTS --------------------

\section{Projects}

\resumeSubHeadingListStart

% Project 1

\resumeProjectHeading
{\textbf{Scopuz} $|$
\footnotesize\emph{React, FastAPI, MongoDB, Docker}}
{
\faIcon{github}
\href{https://github.com/aditzz073/hallucinate-pinnacle}
{\underline{Repo}}
\hspace{6pt}
\faIcon{link}
\href{https://frontend-ten-sooty-84.vercel.app}
{\underline{Demo}}
}

\resumeItemListStart

\resumeItem{Developed an AI-powered SaaS platform to analyze webpage visibility and optimization across AI systems including ChatGPT, Gemini, Claude, and Perplexity.}

\resumeItem{Designed and integrated multiple workflows including audit systems, monitoring modules, analytics dashboards, and scoring mechanisms.}

\resumeItem{Implemented reporting and analysis capabilities to generate actionable insights and support data-driven decision-making.}

\resumeItemListEnd


% Project 2

\resumeProjectHeading
{\textbf{EmberEye: AI-Powered Wildfire Risk Prediction} $|$
\footnotesize\emph{Tensorflow, CNN, FastAPI, Python}}
{
\faIcon{github}
\href{https://github.com/aditzz073/ember-eye}
{\underline{Repo}}
\hspace{6pt}
\faIcon{link}
\href{https://embereye-three.vercel.app/}
{\underline{Demo}}
}

\resumeItemListStart

\resumeItem{Led development of a wildfire risk prediction system involving data collection, model development, API integration, and dashboard deployment.}

\resumeItem{Coordinated machine learning and backend workflows to support analysis and visualization of risk indicators.}

\resumeItem{Built data-driven systems enabling proactive insights and informed decision-making.}

\resumeItemListEnd


% Project 3

\resumeProjectHeading
{\textbf{Pharma Trace} $|$
\footnotesize\emph{React Flow, FastAPI, PostgreSQL, Redis}}
{
\faIcon{github}
\href{https://github.com/aditzz073/supply-chain}
{\underline{Repo}}
\hspace{6pt}
\faIcon{link}
\href{YOUR_DEMO_LINK}
{\underline{Demo}}
}

\resumeItemListStart

\resumeItem{Developed an AI-powered pharmaceutical supply chain platform for generating and visualizing knowledge graphs.}

\resumeItem{Integrated search workflows, structured data pipelines, and caching mechanisms to organize supplier and supply chain information.}

\resumeItem{Implemented interactive visualization and reporting features to support analysis and informed decision-making.}

\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}
